\pdfbookmark[0]{English title page}{label:titlepage_en}
\aautitlepage{%
  \englishprojectinfo{
    Distributed Speech Recognition System %title
  }{%
<<<<<<< HEAD
    Machine Learning & Distributed Systems %theme
=======
    Machine Learning \& Distributed Systems %theme
>>>>>>> ec084b8e9f32c910495c20502810dd230c884e9e
  }{%
    Fall Semester 2017 %project period
  }{%
    ED5-1-E17 % project group
  }{%
    %list of group members
    Stefan Bîrs\\
    Tiberiu-Ioan Szatmari\\
    Kamran Thomas Alimagham
    
  }{%
    %list of supervisors
    Daniel Ortiz-Arroyo\\
    D. M. Akbar Hussain
  }{%
    1 % number of printed copies
  }{%
    \today % date of completion
  }%
}{%department and address
  \textbf{ The Faculty of \\Engineering and Science}\\
  Aalborg University\\
  \href{http://www.en.aau.dk}{http://www.en.aau.dk}
}{% the abstract
  This report goes into detail on the
  implementation of a distributed speech
  recognition system using artificial neural networks.
  A historical overview is presented on
  the different methods used in machine learning. 
  Furthermore, neural network fundamentals
  for achieving a practical
  model for speech recognition are explained.
  Various pre-processing algorithms were developed, 
  one of which being a .flac to .wav file converter
  used to create larger data sets for training.
  The Mel Frequency Cepstrum was used as a
  filter and pre-processing technique.
  All of the above mentioned steps were used to pursue a neural network with a 
  bi-directional LSTM layer and fully connected layers. 
  Following, a client-server framework was developed to distribute the obtained model.
  The report encapsulates the entire process 
  for achieving a fully operational system.
}

\cleardoublepage
